Illusion Game Validation (Study 3)

### 2022-09-06 study3/study3.Rmd
update

cache <- TRUE
runModels <- FALSE
bestModels <- FALSE
fig.width <- see::golden_ratio(7)
fig.height <- 7

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 450,
  fig.path = "./figures/",
  fig.width = fig.width,
  fig.height = fig.height
)
```

@@

# Variables
DVs <- c("Delboeuf" = "#2196F3", 
         "Ebbinghaus" = "#3F51B5", 
         "RodFrame" = "#F44336", 
         "VerticalHorizontal" = "#FF5722", 
         "Zollner" = "#FF9800", 
         "White" = "#9E9E9E", 
         "MullerLyer" = "#4CAF50", 
         "Ponzo" = "#009688", 
         "Poggendorff" = "#795548", 
         "Contrast" = "#607D8B", 
         "I" = "#9C27B0")

# Load data
dfsub <- read.csv("../data/study3.csv") |>
  mutate(
    Screen_Refresh = as.numeric(Screen_Refresh),
    Education = fct_relevel(Education, "High School", "Bachelor", "Master", "Doctorate", "Other", "Prefer not to Say")
  ) |> 
  datawizard::standardise(select=names(DVs))

dflong <- dfsub |> 
  pivot_longer(all_of(names(DVs)), names_to = "Index", values_to = "Score")
# plot(estimate_density(dfsub[DVs]))
```

## Results

### Contextual

#### Screen Size

```{r message=FALSE, warning=FALSE, cache=cache}
preds <- data.frame()
for(i in names(DVs)) {
  model <- brms::brm(paste0(i, " ~ s(Screen_Size)"), data=dfsub, algorithm = "meanfield", refresh=0)
  param <- bayestestR::describe_posterior(as.data.frame(model))

  pred <- estimate_relation(model, length=50)
  pred$Index <- i
  pred$sig <- estimate_slopes(model, trend = "Screen_Size")$pd
  preds <- rbind(preds, pred)

  if(any(pred$sig > .95)) {
    print(i)
  }
}

preds |> 
  mutate(sig = format_pd(sig, stars_only = TRUE),
         sig = ifelse(sig == "", "NS", sig)) |> 
  ggplot(aes(x = Screen_Size, y = Predicted)) +
  geom_point2(data=dflong, aes(y = Score, color= Index), alpha=0.1, size=2) +
  geom_line(aes(color = Index, group = Index, linetype = sig, size = sig)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1, "**" = 1.5)) +
  scale_linetype_manual(values = c("NS" = "dotted", "*" = "dashed", "**" = "solid")) +
  scale_color_manual(values = DVs) +
  coord_cartesian(ylim = c(-2.5, 2.5)) +
  theme_modern() +
  labs(y = "Illusion Sensitivity", x = "Screen Size") +
  ggside::geom_xsidedensity(data=dfsub, fill ="grey", color = "white") +
  ggside::geom_ysidedensity(data=dflong, aes(y=Score, color = Index)) +
  ggside::theme_ggside_void() 
```

#### Refresh Rate

```{r message=FALSE, warning=FALSE, cache=cache}
sig <- list()
preds <- data.frame()
for(i in DVs) {
  model <- brms::brm(paste0(i, " ~ poly(Screen_Refresh, 2)"), data=dfsub, algorithm = "meanfield", refresh=0)
  param <- bayestestR::describe_posterior(as.data.frame(model))

  pred <- estimate_relation(model, length=50)
  pred$Index <- i
  pred$sig <- max(param$pd[2:3])
  preds <- rbind(preds, pred)

  if(any(max(param$pd[2:3]) > .95)) {
    print(i)
  }
}

preds |> 
  mutate(sig = format_pd(sig, stars_only = TRUE),
         sig = ifelse(sig == "", "NS", sig)) |> 
  ggplot(aes(x = Screen_Refresh, y = Predicted)) +
  geom_line(aes(color = Index, group = Index, linetype = sig, size = sig)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1, "**" = 1.5)) +
  scale_linetype_manual(values = c("NS" = "dotted", "*" = "dashed", "**" = "solid"))
```

### Demographics

#### Sex

```{r message=FALSE, warning=FALSE, cache=cache}
sig <- list()
params <- data.frame()
for(i in DVs) {
  model <- lm(paste0(i, " ~ Sex"), data=dfsub)
  param <- parameters::parameters(model)
  param$Index <- i
  param$ymiddle <- param$Coefficient[1] + diff(param$Coefficient) / 2
  params <- rbind(params, as.data.frame(param[2, ]))
  if(param$p[2] < .05) {
    print(i)
  }
}

data <- dfsub |> 
  pivot_longer(all_of(DVs), names_to = "Index", values_to = "Score") |> 
  mutate(Index = fct_relevel(Index, arrange(params, p)$Index))

data |> 
  ggplot(aes(x = Index, y = Score)) +
  stat_slab(data=filter(data, Sex == "Male"), aes(fill = Sex), side = "right", scale = 0.5, position = "dodge") +
  stat_slab(data=filter(data, Sex == "Female"), aes(fill = Sex), side = "left", scale = 0.5, position = "dodge") +
  stat_pointinterval(aes(group = Sex), point_interval = "mean_qi",, position = "dodge") +
  geom_text(data = mutate(params, sig = insight::format_p(p, stars_only = TRUE)), aes(label = sig, y = ymiddle))
```

#### Ethnicity

```{r message=FALSE, warning=FALSE, cache=cache}
sig <- list()
params <- data.frame()
for(i in DVs) {
  model <- lm(paste0(i, " ~ Ethnicity"), data=dfsub)
  param <- estimate_contrasts(model, contrast = "Ethnicity")
  param$Index <- i
  params <- rbind(params, as.data.frame(param[2, ]))
  if(any(param$p < .05)) {
    print(i)
  }
}
```

#### Education

```{r message=FALSE, warning=FALSE, cache=cache}
preds <- data.frame()
for(i in DVs) {
  model <- brms::brm(paste0(i, " ~ mo(as.numeric(Education))"), data=filter(dfsub, !Education %in% c("Other", "Prefer not to Say")), algorithm = "meanfield", refresh=0)
  param <- bayestestR::describe_posterior(as.data.frame(model)["bsp_moas.numericEducation"])

  pred <- estimate_relation(model)
  pred$Index <- i
  pred$sig <- param$pd
  preds <- rbind(preds, pred)

  if(any(param$pd > .95)) {
    print(i)
  }
}

preds |> 
  mutate(sig = format_pd(sig, stars_only = TRUE),
         sig = ifelse(sig == "", "NS", sig)) |> 
  ggplot(aes(x = Education, y = Predicted)) +
  geom_line(aes(color = Index, group = Index, linetype = sig, size = sig)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1, "**" = 1.5)) +
  scale_linetype_manual(values = c("NS" = "dotted", "*" = "dashed", "**" = "solid"))
```

#### Age

```{r message=FALSE, warning=FALSE, cache=cache}
sig <- list()
preds <- data.frame()
for(i in DVs) {
  model <- brms::brm(paste0(i, " ~ poly(Age, 2)"), data=dfsub, algorithm = "meanfield", refresh=0)
  param <- bayestestR::describe_posterior(as.data.frame(model))

  pred <- estimate_relation(model, length=50)
  pred$Index <- i
  pred$sig <- max(param$pd[2:3])
  preds <- rbind(preds, pred)

  if(any(max(param$pd[2:3]) > .95)) {
    print(i)
  }
}

preds |> 
  mutate(sig = format_pd(sig, stars_only = TRUE),
         sig = ifelse(sig == "", "NS", sig)) |> 
  ggplot(aes(x = Age, y = Predicted)) +
  geom_line(aes(color = Index, group = Index, linetype = sig, size = sig)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1, "**" = 1.5)) +
  scale_linetype_manual(values = c("NS" = "dotted", "*" = "dashed", "**" = "solid"))
```

### Personality

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
r <- correlation::correlation(
  datawizard::data_select(dfsub, DVs),
  select(dfsub, starts_with("IPIP") & !ends_with("_SD")),
  p_adjust = "none",
  sort=TRUE
)

r |>
  mutate(label = paste0(format_value(r, zap_small = TRUE), insight::format_p(p, stars_only=TRUE))) |> 
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = r)) +
  geom_text(aes(label=label), size=3) +
  scale_alpha_continuous(range = c(1, 0.5)) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  # facet_wrap(~Illusion_Type, scales = "free") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))
```

>>>>

cache <- TRUE
fig.width <- see::golden_ratio(7)
fig.height <- 7

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  fig.path = "./figures/",
  fig.width = fig.width,
  fig.height = fig.height
)
```

@@

source("../study2/functions.R")

# Variables
DVs <- c(
  "Delboeuf" = "#2196F3",
  "Ebbinghaus" = "#3F51B5",
  "RodFrame" = "#F44336",
  "VerticalHorizontal" = "#FF5722",
  "Zollner" = "#FF9800",
  "White" = "#9E9E9E",
  "MullerLyer" = "#4CAF50",
  "Ponzo" = "#009688",
  "Poggendorff" = "#795548",
  "Contrast" = "#607D8B",
  "i" = "#9C27B0"
)

# Load data
dfsub <- read.csv("../data/study3.csv") |>
  mutate(
    Screen_Refresh = as.numeric(Screen_Refresh),
    Ethnicity = ifelse(Ethnicity == "Latino", "Hispanic", Ethnicity),
    Education = fct_relevel(Education, "High School", "Bachelor", "Master", "Doctorate", "Other", "Prefer not to Say")
  ) |>
  datawizard::standardise(select = names(DVs)) |>
  datawizard::change_scale(select = starts_with("IPIP"), to = c(0, 1), range = c(0, 100)) |>
  datawizard::change_scale(select = starts_with("PID"), to = c(0, 1), range = c(0, 100))

# Remove outliers (p < 0.0001)
dfsub[names(DVs)][abs(dfsub[names(DVs)]) > qnorm(0.9999)] <- NA

dflong <- dfsub |>
  pivot_longer(all_of(names(DVs)), names_to = "Index", values_to = "Score")
```

## Participants

`r sum(is.na(dfsub$IPIP6_Agreeableness))` participants did not do the personality scales.

```{r demographics}
p_age <- estimate_density(dfsub$Age) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(fill = "#607D8B") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Age", color = NULL) +
  theme_modern() +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    plot.subtitle = element_text(face = "italic", hjust = 0.5),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.x = element_blank()
  )

p_nat <- dfsub |>
  group_by(Nationality) |>
  summarize(n = n()) |>
  mutate(Nationality = fct_reorder(Nationality, desc(n))) |>
  ggplot(aes(x = Nationality, y = n, fill = Nationality)) +
  geom_bar(stat = "identity") +
  labs(y = "Number", title = "Nationality") +
  scale_fill_material_d(guide = "none") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_modern() +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    plot.subtitle = element_text(face = "italic", hjust = 0.5),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_text(size = rel(0.8)),
    axis.text.x = element_text(size = rel(0.6), angle = 50, hjust = 1)
  )

# ggsave("figures/figure_dem1.png",
#        patchwork::wrap_elements(p_age / p_nat),
#        width=0.5*(fig.height),
#        height=1*(fig.height), dpi=1000, bg="white")

p_sex <- plot_waffle(dfsub, what = "Sex", rows = 10, size = 5) +
  scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63"))

p_edu <- plot_waffle(dfsub, "Education", rows = 10, size = 5) +
  scale_color_viridis_d()

p_race <- plot_waffle(dfsub, "Ethnicity", rows = 10, size = 5) +
  scale_color_manual(values = c("Hispanic" = "#FF5722", "Caucasian" = "#2196F3", "African" = "#4CAF50", "Other" = "#795548"))

# ggsave("figures/figure_dem2.png",
#        patchwork::wrap_elements(p_sex / p_edu / p_race), width=1*(fig.height), height=1*(fig.height), dpi=1000, bg="white")

p_ipip <- dfsub |>
  select(starts_with("IPIP") & !ends_with("_SD")) |>
  estimate_density() |>
  mutate(
    Parameter = str_remove_all(Parameter, "IPIP6_"),
    Parameter = str_replace(Parameter, "HonestyHumility", "Honesty-Humility")
  ) |>
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line(size = 1) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(values = c("Agreeableness" = "#FFC107", "Honesty-Humility" = "#00BCD4", "Extraversion" = "#9C27B0", "Conscientiousness" = "#3F51B5", "Openness" = "#4CAF50", "Neuroticism" = "#E91E63")) +
  labs(x = "Score", title = "Normal Personality", color = NULL) +
  theme_modern() +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.x = element_blank(),
    legend.text = element_text(size = rel(0.8))
  )

p_pid <- dfsub |>
  select(starts_with("PID") & !ends_with("_SD")) |>
  estimate_density() |>
  mutate(
    Parameter = str_remove_all(Parameter, "PID5_"),
    Parameter = str_replace(Parameter, "NegativeAffect", "Negative Affect")
  ) |>
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line(size = 1) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(values = c("Antagonism" = "#FF9800", "Detachment" = "#03A9F4", "Disinhibition" = "#FF5722", "Negative Affect" = "#F44336", "Psychoticism" = "#673AB7")) +
  labs(x = "Score", title = "Pathological Personality", color = NULL) +
  theme_modern() +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.x = element_blank(),
    legend.text = element_text(size = rel(0.8))
    # legend.position = "top",
  )

# ggsave("figures/figure_dem3.png",
#        patchwork::wrap_elements(p_ipip / p_pid), width=2/3*(fig.height), height=1*(fig.height), dpi=1000, bg="white")

p_dem <- (
  patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_dem1.png"), interpolate = TRUE)) |
    patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_dem2.png"), interpolate = TRUE)) |
    patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_dem3.png"), interpolate = TRUE))
) +
  patchwork::plot_layout(widths = c(1 / 2, 1, 2 / 3))

p_dem +
  patchwork::plot_annotation(
    title = "Participants (n = 250)",
    theme = theme(plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0.5, vjust = -10))
  )
```
```{r eval=FALSE}
# Run this manually to avoid saving margins
ggsave("figures/figure_dem.png", p_dem +
  patchwork::plot_annotation(
    title = "Participants (n = 250)",
    theme = theme(plot.title = element_text(size = 50, face = "bold", hjust = 0.5, vjust = 0))
  ), height = 7200, width = 15166, units = "px", limitsize = FALSE)
```

# Results

## Contextual

```{r message=FALSE, warning=FALSE, cache=cache}
make_correlation <- function(x, y) {
  cor <- correlation::correlation(x,
    y,
    bayesian = TRUE,
    bayesian_prior = "medium.narrow",
    sort = TRUE
  ) |>
    datawizard::data_remove(c("ROPE_Percentage"))
  cor$`BF (Spearman)` <- format_bf(
    correlation::correlation(
      x, y,
      bayesian = TRUE,
      ranktransform = TRUE,
      bayesian_prior = "medium.narrow"
    )$BF,
    name = NULL, stars = TRUE
  )
  cor |>
    arrange(desc(BF))
}

make_correlation(dfsub[names(DVs)], dfsub[c("Screen_Size", "Screen_Refresh")])

dflong |>
  ggplot(aes(x = Screen_Size, y = Score)) +
  geom_point2(aes(color = Index), alpha = 0.1, size = 2) +
  geom_smooth(aes(color = Index, group = Index, linetype = Index), se = FALSE, method = "lm") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1)) +
  scale_linetype_manual(values = c("White" = "solid", "Contrast" = "solid", setNames(rep("dotted", 9), names(DVs)[!names(DVs) %in% c("White", "Contrast")])), guide = "none") +
  scale_color_manual(values = DVs) +
  theme_modern() +
  labs(y = "Illusion Sensitivity", x = "Screen Size", linetype = "Significance", size = "Significance") +
  ggside::geom_xsidedensity(data = dfsub, fill = "grey", color = "white") +
  ggside::geom_ysidedensity(aes(y = Score, color = Index)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0))
```

## Demographics

### Sex

```{r message=FALSE, warning=FALSE, cache=cache}
sig <- list()
params <- data.frame()
for (i in names(DVs)) {
  model <- lm(paste0(i, " ~ Sex"), data = dfsub)
  param <- parameters::parameters(model)
  param$Index <- i
  param$ymiddle <- param$Coefficient[1] + diff(param$Coefficient) / 2
  param$BF <- parameters::parameters(BayesFactor::ttestBF(formula = as.formula(paste0(i, " ~ Sex")), data = dfsub[!is.na(dfsub[[i]]), ]))$BF
  params <- rbind(params, as.data.frame(param[2, ]))
}

data <- dfsub |>
  pivot_longer(all_of(names(DVs)), names_to = "Index", values_to = "Score") |>
  mutate(
    Index = fct_relevel(Index, names(DVs)),
    Index = fct_relabel(Index, ~ prettify_itemName(.x))
  )

# parameters::parameters(BayesFactor::ttestBF(formula=Zollner ~ Sex, data=dfsub[!is.na(dfsub[[i]]), ]))

p_gender <- data |>
  ggplot(aes(x = Index, y = Score)) +
  stat_slab(data = filter(data, Sex == "Male"), aes(fill = Sex), side = "left", scale = 0.5, position = "dodge") +
  stat_slab(data = filter(data, Sex == "Female"), aes(fill = Sex), side = "right", scale = 0.5, position = "dodge") +
  stat_pointinterval(aes(group = fct_rev(Sex)), point_interval = "mean_qi", position = "dodge") +
  geom_text(data = mutate(params, sig = insight::format_bf(BF, stars_only = TRUE), Index = prettify_itemName(Index)), aes(label = sig, y = ymiddle), size = 6) +
  geom_label(
    data = mutate(params, label = insight::format_bf(BF, protect_ratio = TRUE), Index = prettify_itemName(Index)),
    aes(label = label), y = 2.7, size = 3
  ) +
  scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
  scale_x_discrete(labels = function(x) ifelse(x == "i", "Factor i", x)) +
  theme_minimal() +
  labs(fill = "", x = "Sex", y = "Illusion Sensitivity", title = "Sex") +
  theme(
    legend.position = "top",
    axis.title.x = element_blank(),
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5)
  )

p_gender
# ggsave("figures/figure_sex.png", p_gender, width=15166, height=5000, bg="white", units = "px", limitsize = FALSE, scale = 0.3)
```

### Education

```{r message=FALSE, warning=FALSE, cache=cache}
preds <- data.frame()
for (i in names(DVs)) {
  model <- brms::brm(paste0(i, " ~ mo(as.numeric(Education))"), data = filter(dfsub, !Education %in% c("Other", "Prefer not to Say")), refresh = 0)
  param <- bayestestR::describe_posterior(as.data.frame(model)["bsp_moas.numericEducation"])

  pred <- estimate_relation(model)
  pred$Index <- i
  pred$sig <- param$pd
  preds <- rbind(preds, pred)
}

preds |>
  mutate(
    sig = format_pd(sig, stars_only = TRUE),
    sig = ifelse(sig == "", "NS", sig)
  ) |>
  ggplot(aes(x = Education, y = Predicted)) +
  geom_line(aes(color = Index, group = Index, linetype = sig, size = sig)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1)) +
  scale_linetype_manual(values = c("NS" = "dotted", "*" = "solid")) +
  theme_modern()
```

### Age

```{r message=FALSE, warning=FALSE, cache=cache}
preds <- data.frame()
for (i in names(DVs)) {
  gam <- brms::brm(paste0(i, " ~ s(Age, k=3)"), data = dfsub, refresh = 0, seed = 1)
  model <- brms::brm(paste0(i, " ~ poly(Age, 2)"), data = dfsub, refresh = 0, seed = 1)

  param <- parameters::parameters(model)
  slopes <- estimate_slopes(gam, trend = "Age")

  pred <- get_datagrid(gam, at = "Age", length = 50)
  pred$Predicted <- get_predicted(gam, data = pred)

  pred$ylabel <- pred$Predicted[50]
  pred$Index <- i
  pred$Effect <- slopes$Coefficient
  pred$pd_gam <- slopes$pd
  pred$pd_poly1 <- param$pd[2]
  pred$pd_poly2 <- param$pd[3]
  preds <- rbind(preds, pred)
}

preds |>
  group_by(Index) |>
  slice(1) |>
  select(-Predicted, -Age) |>
  arrange(desc(pd_gam))

p_age <- preds |>
  mutate(
    pd_gam = format_pd(pd_gam, stars_only = TRUE),
    pd_gam = ifelse(pd_gam == "", "NS", pd_gam)
  ) |>
  ggplot(aes(x = Age, y = Predicted)) +
  geom_line(aes(color = Index, group = Index, linetype = pd_gam, size = pd_gam)) +
  ggrepel::geom_label_repel(
    data = preds |>
      group_by(Index) |>
      slice(1) |>
      mutate(label = prettify_itemName(ifelse(Index == "i", "Factor i", Index))),
    aes(y = ylabel, label = label, x = 69, color = Index), hjust = 0, direction = "y",
    min.segment.length = 3
  ) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1, "**" = 1, "***" = 1)) +
  scale_linetype_manual(values = c("NS" = "dotted", "*" = "solid", "**" = "solid", "***" = "solid")) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_color_manual(values = DVs) +
  guides(size = "none", linetype = "none", color = "none") +
  theme_modern() +
  labs(y = "Illusion Sensitivity", title = "Age") +
  theme(
    legend.position = "top",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5)
  )

p_age

ggsave("figures/figure_agesex.png",
  (p_gender + p_age) + plot_layout(widths = c(2 / 3, 1 / 3)) +
    patchwork::plot_annotation(
      title = "Illusion Sensitivity and Demographic Variables",
      theme = theme(plot.title = element_text(size = rel(1.5), face = "bold", hjust = 0.5, vjust = 0))
    ),
  width = 15166, height = 5000, bg = "white", units = "px", limitsize = FALSE, dpi = 800, scale = 1
)
```

## Personality

### IPIP6

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
cor <- make_correlation(
  datawizard::data_select(dfsub, names(DVs)),
  select(dfsub, starts_with("IPIP") & !ends_with("_SD"))
)

cor |>
  data_filter(BF > 1) |>
  arrange(desc(BF))

cor |>
  mutate(
    label = paste0(format_value(rho, zap_small = TRUE), insight::format_bf(BF, stars_only = TRUE)),
    Parameter2 = prettify_parameterName(Parameter2),
    Parameter2 = str_remove_all(Parameter2, "IPIP6 - ")
  ) |>
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = rho)) +
  geom_text(aes(label = label), size = 3) +
  scale_alpha_continuous(range = c(1, 0.5)) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  labs(y = "Illusion Sensitivity Scores", x = "Normal Personality (IPIP6)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p_ipip1 <- plot_correlation(dfsub, x = "i", y = "IPIP6_Agreeableness", fill = "#FFC107")
p_ipip2 <- plot_correlation(dfsub, x = "i", y = "IPIP6_HonestyHumility", fill = "#00BCD4")

(p_ipip1 + plot_correlation(dfsub, x = "VerticalHorizontal", y = "IPIP6_Agreeableness", fill = "#FFC107") + plot_correlation(dfsub, x = "Ponzo", y = "IPIP6_Agreeableness", fill = "#FFC107")) /
  (p_ipip2 + plot_correlation(dfsub, x = "Zollner", y = "IPIP6_HonestyHumility", fill = "#00BCD4") + plot_correlation(dfsub, x = "VerticalHorizontal", y = "IPIP6_HonestyHumility", fill = "#00BCD4"))
```

### PID-5

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
cor <- make_correlation(
  datawizard::data_select(dfsub, names(DVs)),
  select(dfsub, starts_with("PID") & !ends_with("_SD"))
)

cor |>
  data_filter(BF > 1) |>
  arrange(desc(BF))

cor |>
  mutate(label = paste0(format_value(rho, zap_small = TRUE), insight::format_bf(BF, stars_only = TRUE))) |>
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = rho)) +
  geom_text(aes(label = label), size = 3) +
  scale_alpha_continuous(range = c(1, 0.5)) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p_pid1 <- plot_correlation(dfsub, x = "i", y = "PID5_Antagonism", fill = "#FF9800")
p_pid2 <- plot_correlation(dfsub, x = "i", y = "PID5_Disinhibition", fill = "#FF5722")
p_pid3 <- plot_correlation(dfsub, x = "i", y = "PID5_Psychoticism", fill = "#673AB7")
p_pid4 <- plot_correlation(dfsub, x = "i", y = "PID5_NegativeAffect", fill = "#F44336")

(p_pid1 | plot_correlation(dfsub, x = "VerticalHorizontal", y = "PID5_Antagonism", fill = "#FF9800") | plot_correlation(dfsub, x = "Ponzo", y = "PID5_Antagonism", fill = "#FF9800")) / (p_pid2 | p_pid3 | p_pid4)

p_pers <- (p_ipip1 +
  theme(
    axis.title.y = element_text(face = "bold"),
    axis.title.x = element_blank()
  )) /
  (p_ipip2 +
    theme(
      axis.title.y = element_text(face = "bold"),
      axis.title.x = element_blank()
    )) |
  (p_pid1 +
    theme(
      axis.title.y = element_text(face = "bold"),
      axis.title.x = element_blank()
    )) /
    (p_pid2 +
      labs(x = expression("Factor" ~ italic(i))) +
      theme(
        axis.title.y = element_text(face = "bold"),
        axis.title.x = element_text(size = rel(1.5), face = "bold")
      )) |
  (p_pid3 +
    theme(
      axis.title.y = element_text(face = "bold"),
      axis.title.x = element_blank()
    )) /
    (p_pid4 +
      theme(
        axis.title.y = element_text(face = "bold"),
        axis.title.x = element_blank()
      ))

# ggsave("figures/figure_pers.png",
#        p_pers + patchwork::plot_annotation(
#          title = "Illusion Sensitivity and Personality",
#          theme = theme(plot.title = element_text(size = rel(1.5), face="bold", hjust=0.5, vjust=0))),
#        width=15166, height=8000, bg="white", units = "px", limitsize = FALSE, dpi=800, scale = 1)
```

## Table and Figure

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
table1 <- ripip |>
  rbind(rpid) |>
  data_remove(c("ROPE_Percentage", "Prior_Distribution", "Prior_Location", "Prior_Scale", "pd")) |>
  separate(Parameter2, "_", into = c("Scale", "Dimension")) |>
  arrange(Scale, desc(BF)) |>
  filter(BF > 3)

table1 |>
  print_md()

table1 |>
  format_table() |>
  select(-Method, -n_Obs) |>
  rename(Factor = Parameter1) |>
  write.csv("table1.csv", row.names = FALSE)
```

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p <- patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_dem.png"), interpolate = TRUE)) /
  patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_agesex.png"), interpolate = TRUE)) /
  patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_pers.png"), interpolate = TRUE)) +
  plot_layout(heights = c(7200, 5000, 8000))

ggsave("../figures/figure3.png", p, height = 20200, width = 15166, units = "px", limitsize = FALSE)
```
